### 2024-06-26 conteudo/introduction/intro.tex
Add final work of the 26/06, only needs the initial text of intro now

Given the first phase completion, we would have a validated tool to indentify code duplications in the Linux kernel 
context and we can move on to how mitigate these duplications, which comprehend the second phase of our research. On the 
\textbf{Phase 2}, we intend to discover ways to mitigate the code duplication detected in the linux kernel. 
To achieve our objective, we designed a etchnographic approach, which enables us to interact with the linux community
to collect artifacts validating or refuting our mitigation. The detailed explication of the etchnographic approach is demonstrated
in the Chatper \ref{cha:method}.

(POINTS TO CONSIDER: I do not like much this introduction, but is the best I could do)
(I DO NOT HAVE MORE A PLACE TO FIT THIS PARAGRAPH) An additional usefulness of our proposed approach, which we do not verify in our research, is to give a new method to people become 
contributors to the Linux kernel. The process of starting to contribute to the Linux kernel can be unintuitive, which can cause 
people to distance themselves. Our approach provides to the community a new form of newcomers to start contributing by removing 
simple code duplications, while they learn the whole process of being a Linux contribuitor.

@@

>>>>

Given the first phase completion, we would have a validated tool to indentify code duplications in the Linux kernel 
context and we can move on to how mitigate these duplications, which comprehend the second phase of our research. On the 
\textbf{Phase 2}, we intend to discover ways to mitigate the code duplication detected in the linux kernel. 
To achieve our objective, we designed a etchnographic approach, which enables us to interact with the linux community
to collect artifacts validating or refuting our mitigation. The figure (CREATE A FIGURE HERE) ilustrate the research
process we addopted in this research.

(POINTS TO CONSIDER: I do not like much this introduction, but is the best I could do)
(I DO NOT HAVE MORE A PLACE TO FIT THIS PARAGRAPH) An additional usefulness of our proposed approach, which we do not verify
in our research, is to give a new method to people become 
contributors to the Linux kernel. The process of starting to contribute to the Linux kernel can be unintuitive, which can cause 
people to distance themselves. Our approach provides to the community a new form of newcomers to start contributing by removing 
simple code duplications, while they learn the whole process of being a Linux contributor.

@@

This manuscript consists of four more chapters. 
Chapter \ref{cha:back} presents the literature overview for the code duplication detection (main definitions, current approches 
methods in the literature), a briefly description of the Linux kernel and a review of refactoring methods used throughtout 
this research.
Chapter \ref{cha:tool} presents our proposed tool to detect code duplication in the Linux kernel, describing all of the main 
components.
Chapter \ref{cha:method} describes the research methods selected to guide our work.
Chapter \ref{cha:results} presents the current research stage and the work plan, with addition of preliminary results obtained.
